\documentclass[10pt,a4paper,withhyper,ragged2e]{altacv}

\geometry{left=1.35cm,right=1.35cm,top=1.4cm,bottom=1.4cm,columnsep=1.15cm}
\usepackage{paracol}

\iftutex
  \setmainfont{Roboto Slab}
  \setsansfont{Lato}
  \renewcommand{\familydefault}{\sfdefault}
\else
  \usepackage[rm]{roboto}
  \usepackage[defaultsans]{lato}
  \renewcommand{\familydefault}{\sfdefault}
\fi

\definecolor{SlateGrey}{HTML}{273043}
\definecolor{LightGrey}{HTML}{5B6472}
\definecolor{DeepBlue}{HTML}{173753}
\definecolor{AccentBlue}{HTML}{28666E}
\definecolor{SoftGold}{HTML}{D9B26F}
\colorlet{name}{black}
\colorlet{tagline}{AccentBlue}
\colorlet{heading}{DeepBlue}
\colorlet{headingrule}{SoftGold}
\colorlet{subheading}{AccentBlue}
\colorlet{accent}{AccentBlue}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\footnotesize}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}
\renewcommand{\cvItemMarker}{{\small\textbullet}}
\renewcommand{\cvRatingMarker}{\faCircle}

\begin{document}

\name{Ashwini Chaudhary}
\tagline{CTO \textbar\ Hands-on Engineering Leader \textbar\ Backend, Platform \& AI Systems}

% Header design notes
% -------------------
% We keep the most important contact points in the top header because readers
% often scan only the first screen/page.
%
% The built-in AltaCV helpers (`\email`, `\phone`, `\homepage`, `\github`)
% are intentionally used here because they include the correct hyperlink target.
% Our patched `\printinfo` implementation keeps the spacing *outside* the link
% box, which gives PDF viewers tighter, more accurate clickable regions.
\personalinfo{%
  \email{monty.sinngh@gmail.com}
  \phone{+16478641745}
  \location{Toronto, Canada}
  \homepage{ashwch.com}
  \github{ashwch}
}

\makecvheader

% Layout note
% -----------
% AltaCV uses two flowing columns via `paracol`.
% We bias slightly wider to the left because the experience section carries the
% highest information density, while the right column is intentionally concise.
\columnratio{0.6}
\begin{paracol}{2}

% Content structure notes
% -----------------------
% This resume is intentionally front-loaded.
%
% First principles:
% - busy readers decide very quickly whether to keep reading
% - the current CTO role carries the highest signal
% - older roles should support the story, not compete with it
%
% So the order is:
% 1. short profile for positioning
% 2. current/high-impact work first
% 3. public credibility (writing / OSS / Stack Overflow)
% 4. supporting older experience and education
\cvsection{Profile}

Hands-on CTO with 12+ years across backend systems, payments, platform engineering, reliability, security, and AI-enabled internal tooling. I lead teams, shape technical direction, hire and mentor engineers, and still work deeply as an individual contributor on architecture, infrastructure, migrations, developer tooling, and other high-leverage technical initiatives. My work sits at the intersection of product delivery, platform engineering, software quality, and practical AI adoption.

\cvsection{Experience}

% Highest-signal section
% ----------------------
% This role should answer the question:
% "Why is this person operating at CTO scope today?"
%
% The bullets therefore mix:
% - product/platform ownership
% - cost/security/compliance responsibility
% - people leadership
% - continued hands-on IC depth
\cvevent{Chief Technology Officer}{Diversio Inc}{Jul 2024 -- Present}{Toronto}
\begin{itemize}
\item Lead Diversio's pivot to Optimo while continuing to maintain, simplify, and evolve the core Diversio product.
\item Own engineering across architecture, infrastructure, reliability, security, internal tooling, engineering quality, and long-term technical strategy.
\item Remain a highly hands-on technical leader, contributing directly to architecture, infrastructure, migrations, developer tooling, security, and other critical engineering initiatives.
\item Reduced maintenance cost by simplifying systems, improving maintainability, and making the platform easier for engineers to operate.
\item Led cost-cutting, vendor rationalization, and a successful SR\&ED round that secured savings for Diversio.
\item Negotiated and maintained critical software vendors and services used across the company.
\item Led migration of the API workflow from Postman to Bruno; the resulting blog post was later featured in Bruno's marketing.
\item Managed career progression, mentoring, code review standards, and day-to-day technical leadership across engineering.
\item Hired and mentored many co-op students in Canada, including from the University of Toronto, Queen's University, the University of Waterloo, and other top programs.
\end{itemize}

\divider

% Progression note
% ----------------
% We keep the internal title progression at Diversio explicit because it shows a
% clean path from early engineering hire -> lead -> HoE -> CTO.
\cvevent{Head of Engineering}{Diversio Inc}{Jul 2023 -- Jun 2024}{Toronto}
\begin{itemize}
\item Led engineering execution across teams through hiring, mentoring, delivery improvements, internal tooling, and stronger engineering standards.
\item Directed major platform and stack consolidation work following Diversio's acquisition of CCDI Consulting Inc.
\item Strengthened development workflows and cross-team delivery practices while keeping core systems maintainable.
\end{itemize}

\divider

\cvevent{Lead Engineer}{Diversio Inc}{Aug 2019 -- Jun 2023}{Toronto / Remote}
\begin{itemize}
\item Early engineering hire who helped build core backend systems and infrastructure across multiple products.
\item Owned infrastructure using Terraform and Terragrunt, along with deployments, production operations, and platform capabilities.
\item Led successful SOC 2 work and supported multiple penetration testing rounds and related remediation.
\item Built internal developer tooling and engineering processes that improved productivity and delivery.
\end{itemize}

\divider

% Older roles are intentionally compressed.
% They establish long-term depth in infrastructure, backend systems, and
% performance work, but should not crowd out the current leadership story.
\cvevent{Software Engineer}{Unhaggle Inc}{Nov 2017 -- Feb 2021}{Remote}
\begin{itemize}
\item Owned infrastructure, site reliability, and deployments for the Dealer team.
\item Built internal tools that improved developer productivity and delivery.
\item Delivered application performance improvements in Python and PostgreSQL.
\end{itemize}

\divider

\cvevent{Senior Software Engineer}{Instamojo}{Mar 2015 -- Oct 2017}{Bengaluru}
\begin{itemize}
\item Led backend work on card processing and storage projects.
\item Built and maintained Instamojo's e-commerce plugins and SDKs across WordPress, OpenCart, PrestaShop, Magento, Drupal, MeteorJS, CS-Cart, WHMCS, and Python/Ruby/PHP wrappers.
\item Delivered key features including KYC onboarding, Orders API, payment gateway integrations, social login, and automated refunds.
\item Helped port the main application from Python 2 to Python 3 and improve performance across Postgres, Django, and Python.
\item Added code quality hooks using flake8, Mypy, Golint, and Vet.
\end{itemize}

\divider

\cvevent{Python Developer}{Simform Solutions}{Sep 2013 -- Feb 2015}{Ahmedabad}
\begin{itemize}
\item Built the real-time backend for SentMap using Node.js, Socket.IO, and Express to stream market and sentiment data over WebSockets.
\item Implemented 3D frontend charting in three.js and 2D charting in Highcharts.
\item Built API backends for Breakup RX App and Minho App using Django and Django REST Framework.
\item Wrote group chat infrastructure for both apps using Twisted.
\end{itemize}

% Public credibility section
% -------------------------
% This section exists because the resume should not rely only on self-description.
% Writing, OSS, speaking, and Stack Overflow provide external proof of technical
% depth and long-term engagement with the craft.
\cvsection{Writing \& Community}

\cvevent{Selected writing}{}{}{}
\begin{itemize}
\item \href{https://ashwch.com/how-we-use-ai-like-engineers.html}{How We Use AI Like Engineers}
\item \href{https://ashwch.com/no-code-by-hand-agentic-platform-acceleration.html}{No Code by Hand: Agentic Platform Acceleration}
\item \href{https://ashwch.com/from-postman-to-bruno-how-ai-changed-our-api-workflow.html}{From Postman to Bruno: How AI Changed Our API Workflow}
\item \href{https://ashwch.com/protecting-our-own-tenant-in-a-multi-tenant-saas.html}{Protecting Our Own Tenant in a Multi-Tenant SaaS}
\item \href{https://ashwch.com/insights-from-everything-i-know-about-good-system-design.html}{Insights From Everything I Know About Good System Design}
\end{itemize}

\divider

\cvevent{Open source, speaking \& community}{}{}{}
\begin{itemize}
\item Contributed to the Python ecosystem through typeshed, mypy, django-debug-toolbar, pep8speaks, django-annoying, pgmpy, and related projects.
\item Built Instamojo payment SDKs and e-commerce plugins across Python, PHP, Ruby, Java, and .NET.
\item Built public tooling including auto-uv-env, precommit-vet-lint, ew, microverse, wt, and agent skills / MCP-related projects.
\item Answered 3,700+ Python questions on Stack Overflow, spoke at MUPy, and coached at Django Girls Bangalore.
\end{itemize}

\switchcolumn

% Right-column design note
% ------------------------
% The right column is intentionally summary-heavy:
% - quick scan of leadership scope
% - current stack/context
% - compact proof points
% - links for follow-up
%
% If this column becomes too dense, reduce items before widening it. The left
% column should remain the primary narrative column.
\cvsection{Leadership Focus}

\begin{itemize}
\item Engineering leadership and technical strategy
\item Backend, platform, and infrastructure architecture
\item Reliability, security, compliance, and operations
\item Hiring, mentoring, career progression, and code quality
\item Developer tooling and internal platform improvements
\item AI-assisted engineering workflows and delivery systems
\end{itemize}

\cvsection{Core Stack}

Python, Django, Postgres, AWS, Terraform, Docker, Redis, Celery, Go, Node.js, Linux, and Git.

\cvsection{Highlights}

\cvachievement{\faUsers}{Team leadership}{Led engineers through hiring, mentoring, technical direction, and review standards.}

\divider

\cvachievement{\faServer}{Platform ownership}{Owned infrastructure, Terraform/Terragrunt, deployments, reliability, and delivery systems.}

\divider

\cvachievement{\faCode}{Technical breadth}{Worked across backend systems, payments, migrations, security, performance, and developer tooling.}

\divider

\cvachievement{\faGlobe}{Public technical profile}{Writer, speaker, open source contributor, and long-time Stack Overflow contributor.}

% Recognition is kept compact and durable.
% We prefer stable, externally legible signals over fragile leaderboard-style
% details that drift every few months.
\cvsection{Recognition}

\begin{itemize}
\item Stack Overflow: 252K reputation, 3,700+ answers, ranked \#287 overall.
\item Unsplash: 207M+ views, 1.2M+ downloads, and top 1000 on the platform.
\item Arctic Code Vault Contributor.
\item Won Instamojo's hackathon for building a payments-powered vending machine.
\end{itemize}

% Education is intentionally minimal.
% At this career stage, it is supporting context rather than a decision-making
% section, so we keep only the highest-signal credential.
\cvsection{Education}

\cvevent{B.Tech. in IT}{IMS Engineering College}{2009 -- 2013}{Ghaziabad}

\cvsection{Links}

% Why use a 2-column table here instead of a bullet list?
% ------------------------------------------------------
% First principles:
% - icons should align vertically
% - each URL should sit on its own row
% - clickable areas should not bleed into the next line
%
% A simple `tabular` gives us predictable icon/text alignment and enough vertical
% spacing that PDF link annotations remain easier to inspect in readers like
% Preview.app.
\begin{tabular}{@{}l l@{}}
\faGlobe & \href{https://ashwch.com}{\strut ashwch.com}\\[0.7em]
\faGithub & \href{https://github.com/ashwch}{\strut github.com/ashwch}\\[0.7em]
\faLinkedin & \href{https://www.linkedin.com/in/ashwch/}{\strut linkedin.com/in/ashwch}\\[0.7em]
\faStackOverflow & \href{https://stackoverflow.com/users/846892/ashwini-chaudhary}{\strut Stack Overflow}\\[0.7em]
\faCamera & \href{https://unsplash.com/@suicide_chewbacca}{\strut Unsplash}
\end{tabular}

\end{paracol}
\end{document}
